\papertitle

### 2013-02-05 manuscript.tex
more references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
Power, size, and weight constraints on 10 gram scale micro air vehicles (MAV) 
significantly limit their sensing and computational capabilities. MAVs can 
execute only low-complexity control and state estimation algorithms in 
real-time.  The constraints on flapping-wing MAVs are even more restrictive. 
Though they demonstrate safety and noise profiles superior to those of 
rotorcraft MAVs, this comes at the expense of reduced payload.

@@

Many control laws researchers have developed from dynamic models of 
flapping-wing flight, such as periodic forcing and other control methods 
described by~\cite{doman:dynamics}\cite{khan:longitudinal_control}\cite{leonard:averaging}, 
require powerful on-board computing. In this work, we develop a simpler, 
less computationally-intensive method of control for negotiating narrow 
passages, by exploiting cooperation between specialized robotic agents.
%

@@

There also exists a body of work on the guidance and control of fixed- and 
rotary-wing MAV platforms, but many of these methods make extensive use of 
GPS or motion capture systems~\cite{kanade:3dvision}\cite{kingston:timeattitude}. 
Indoors, using GPS to estimate the pose of an MAV is unreliable, and motion 
capture requires extensive and stationary modification of the environment. 
The power and payload limits on flapping-wing MAVs make complex on-board 
sensing difficult, so multiagent cooperative control schemes are apt 
solutions.

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et
al. all demonstrated cooperative visual servoing for heterogeneous
UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}.
Luo, et al. and Mehta, et al. analyze UAV-UGV cooperation from a modeling
perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. Rudol et al.
demonstrated a similar cooperative visual servoing system with UGVs and
MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of magnitude
larger than the lightweight systems we target, and so were able to take
advantage of high-performance processors and specialized cameras. Stirling et
al. describe a method for guiding quadrotors, designated as explorers, though
a network of stationary quadrotors, designated as beacons, through an indoor
environment~\cite{SwarmStirling}. The beacons provide external sensing for
navigating the explorers through the environment, and the network can be
extended by using explorers as beacons in undiscovered areas. Their
implementation relies solely on local sensing, although our size range
requires that the actual environment sensing be external to the MAV. Additionally, they do not consider time constraints in their planning, whereas our MAV has a minimum forward speed and turning radius.

@@

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy. The sampling law is as follows:\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In Equation~\ref{eq:motion_model}, $x^{[i]}_t$ is the position of the $i^\text{th}$ 
particle in 640x480 pixel space at time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ 
is a vector of the bounds of the pixel space. The sampling method requires that, with 
probability $\epsilon$, the particle filter will choose a pixel from a uniform 
distribution of all of the pixels in the pixel space for the location of the $i^\text{th}$ 
particle. The $\epsilon$-random uniform transitions increase tracking robustness, by 
forcing the filter to always sample broadly across the pixel space. This helps prevent 
overconfidence and collapse, and decreases reacquisition delay.

@@

%............................................................................%
\subsubsection{Emission Model}
The emission model weights the particles' likelihood of containing a pixel location that is part of the H$^2$Bird. The particles with higher weights have a greater probability of being resampled. Our emission model implements a sampling
approach to motion tracking via na\"{i}ve background subtraction, e.g. frame 
differencing~\cite{Ahad2011Computer}: 
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental setup.}
\label{fig:experiment_cartoon}
\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\begin{figure}[!tb]
\centering
\includegraphics[width=0.95\linewidth]{figures/h2bird.png}
\caption{H$^2$Bird ornithopter MAV}
\label{fig:h2bird}
\end{figure}
Power, size, and weight constraints on 10 gram scale micro air vehicles (MAV) 
significantly limit their sensing and computational capabilities. MAVs can 
execute only low-complexity control and state estimation algorithms in 
real-time.  The constraints on flapping-wing MAVs are even more restrictive. 
Though they demonstrate safety and noise profiles superior to those of 
rotorcraft MAVs, this comes at the expense of reduced payload.

@@

Many control laws researchers have developed from dynamic models of 
flapping-wing flight, such as periodic forcing and other control methods 
described by~\cite{doman:dynamics}\cite{khan:longitudinal_control}\cite{leonard:averaging}, 
require powerful on-board computing. In this work, we develop a simpler, 
less computationally-intensive method of control for negotiating narrow 
passages, by exploiting cooperation between specialized robotic agents.

@@

There also exists a body of work on the guidance and control of fixed- and 
rotary-wing MAV platforms, but many of these methods make extensive use of 
GPS or motion capture systems~\cite{kanade:3dvision}\cite{kingston:timeattitude}. 
Indoors, using GPS to estimate the pose of an MAV is unreliable, and motion 
capture requires extensive and stationary modification of the environment.

The literature on cooperative control of MAVs is similarly limited to larger
vehicles or analytical explorations. Hyams et al., Jung et al. and Nebot et
al. all demonstrated cooperative visual servoing for heterogeneous
UGVs~\cite{Hyams1999Cooperative}\cite{Jung1998Range}\cite{Nebot2003Agents}.
Luo, et al. and Mehta, et al. analyze UAV-UGV cooperation from a modeling
perspective~\cite{Luo2011Air}\cite{Mehta2006Adaptive}. Rudol et al.
demonstrated a similar cooperative visual servoing system with UGVs and
MAVs~\cite{Rudol2008Micro}, but the vehicles used were orders of magnitude
larger than the lightweight systems we target, and so were able to take
advantage of high-performance processors and specialized cameras. Stirling et
al. describe a method for cooperation amonst quadrotor MAVs to navigate indoor
environment~\cite{SwarmStirling}. Stationary MAVs provide external sensing for
navigation through the environment, and the network can be extended by using
the exploring MAVs for sensing in undiscovered areas. Their implementation
relies solely on local sensing, although our size range requires that the
actual environment sensing be external to the MAV. Additionally, they do not
consider time constraints in their planning, whereas our MAV has a minimum
forward speed and turning radius.

@@

We initialize the particles 
uniformly across the frame before tracking begins. To improve numerical 
stability, we normalize the weights of all particles on each iteration, and 
only resample the particle population when the mean particle weight falls 
below a pre-determined threshold. 
%............................................................................%
\subsubsection{Motion Model}
Our motion model (Equation~\ref{eq:motion_model}) is a simple Gaussian transition 
centered around each particle's current position, augmented with an 
$\epsilon$-random uniform sampling strategy~\cite{Doucet2001}. The sampling law is as follows:
\begin{equation}
\label{eq:motion_model}
x^{[i]}_t \sim \begin{cases}
\mathcal{N}(x^{[i]}_{t-1}, \Sigma), &\text{with probability } 1-\epsilon \\
\mathcal{U}(0,b),& \text{with probability } \epsilon \\
\end{cases}\\
\end{equation}
In Equation~\ref{eq:motion_model}, $x^{[i]}_t$ is the position of the $i^\text{th}$ 
particle in 640x480 pixel space at time $t$, $\Sigma$ is a chosen covariance matrix, and $b$ 
is a vector of the bounds of the pixel space. The sampling method requires that, with 
probability $\epsilon$, the particle filter will choose a pixel from a uniform 
distribution of all of the pixels in the pixel space for the location of the $i^\text{th}$ 
particle. The $\epsilon$-random uniform transitions increase tracking robustness, by 
forcing the filter to always sample broadly across the pixel space. This helps prevent 
overconfidence and collapse, and decreases reacquisition delay.

@@

%............................................................................%
\subsubsection{Emission Model}
The emission model weights the particles' likelihood of containing a pixel
location that is part of the H$^2$Bird~\cite{Doucet2001}. The particles with
higher weights have a greater probability of being resampled. Our emission
model implements a sampling approach to motion tracking via na\"{i}ve
background subtraction, e.g. frame differencing~\cite{Ahad2011Computer}:
\begin{equation}
\label{eq:emission_model}
w^{[i]}_t = 1 + \norm{f_0(x^{[i]}_t)-f_t(x^{[i]}_t)}^2
\end{equation} 
On each iteration, the system provides the emission 
model with $f_0$, the frame representing the background, and $f_t$, the most 
recent frame captured. The model assigns a weight $w^{[i]}_t$ to each 
particle $x^{[i]}_t$, proportional to the color distance in RGB space 
between the pixels of $f_0$ and $f_t$ at the location $x^{[i]}_t$.
Hence, particles are more likely to be resampled in regions of 
the image which are dissimilar in color from the background.

@@

\begin{figure}[tb]
\centering
\includegraphics[width=0.9\linewidth]{figures/experiment_cartoon.pdf}
\caption{Conceptual sketch of experimental setup.}
\label{fig:experiment_cartoon}
\end{figure}
